Paper notes

### 2019-08-15 paper_notes.Rmd
Update paper_notes.Rmd

---
output:
  bookdown::pdf_document2:
    toc: false
 #   keep_tex: false
    fig_caption: yes
title: "Paper notes"
author: Rocco Paolillo
bibliography: "references.bib"
# csl: apa.csl # by default: Chicago style
header-includes:
- \usepackage{float}
- \usepackage{multirow}
- \usepackage{xcolor} 
- \usepackage{amsmath}
---

>>>>

---
output:
  bookdown::pdf_document2:
    toc: false
 #   keep_tex: false
    fig_caption: yes
title: "Paper notes"
author: Rocco Paolillo
bibliography: "references.bib"
# target: BIGSSS Research Day by September 15th, presented  on October 25th. 6000 words: around 12 pages.
# csl: apa.csl # by default: Chicago style
header-includes:
- \usepackage{float}
- \usepackage{multirow}
- \usepackage{xcolor} 
- \usepackage{amsmath}
---
